---
title: "Week_1"
output: pdf_document
date: "2022-10-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# library(tinytex)
```

## C1.3

```{r}
monte <- function (n,h) {
  norm1 <- pmax(rnorm(n,mean = 0, sd=1),0)
  norm2 <- pmax(rnorm(n,mean = 0 , sd=1+h),0)
  
  derivative <- 1/h*(mean(norm2)-mean(norm1))
  return(derivative)
}
set.seed(12345)
run_many <- c()
 for (x in 1:10000) {
  it <- monte(1000,h=0.1)
  run_many <- c(run_many,it)
}

bias <- mean(run_many)-1/sqrt(1/2*pi)
eff <- mean((run_many-mean(run_many))^2)
mse <- mean((run_many-1/sqrt(1/2*pi))^2)
```

The random observation has bias `r round(bias,2)`, efficiency `r round(eff,2)` and mean square error `r round(mse,2)`. Setting h closer to 0 would likely reduce bias. 

(ii) Now, use coupling method to define norm1 and norm2.

```{r }
monte1 <- function (n,h) {
  normz <- rnorm(n,mean = 0, sd=1)
  norm1 <- pmax(normz,0)
  norm2 <- pmax(normz*(1+h),0)
  
  derivative <- 1/h*(mean(norm2)-mean(norm1))
  return(derivative)
}
set.seed(12345)
run_many <- c()
 for (x in 1:10000) {
  it <- monte(1000,h=0.1)
  run_many <- c(run_many,it)
}

bias <- mean(run_many)-1/sqrt(1/2*pi)
eff <- mean((run_many-mean(run_many))^2)
mse <- mean((run_many-1/sqrt(1/2*pi))^2)
```

The random observation has bias `r round(bias,2)`, efficiency `r round(eff,2)` and mean square error `r round(mse,2)`.

## Repetition 2: h=0.01

```{r}
set.seed(12345)
run_many <- c()
 for (x in 1:10000) {
  it <- monte1(1000,h=0.01)
  run_many <- c(run_many,it)
}

bias <- mean(run_many)-1/sqrt(1/2*pi)
eff <- mean((run_many-mean(run_many))^2)
mse <- mean((run_many-1/sqrt(1/2*pi))^2)
```
The random observation has bias `r round(bias,2)`, efficiency `r round(eff,2)` and mean square error `r round(mse,2)`.

## Repetition 3: h=0.05
```{r}
set.seed(12345)
run_many <- c()
 for (x in 1:10000) {
  it <- monte1(1000,h=0.05)
  run_many <- c(run_many,it)
}

bias <- mean(run_many)-1/sqrt(1/2*pi)
eff <- mean((run_many-mean(run_many))^2)
mse <- mean((run_many-1/sqrt(1/2*pi))^2)
```
The random observation has bias `r round(bias,2)`, efficiency `r round(eff,2)` and mean square error `r round(mse,2)`.

## Repetition 4: h=0.0001
```{r}
set.seed(12345)
run_many <- c()
 for (x in 1:10000) {
  it <- monte1(1000,h=0.0001)
  run_many <- c(run_many,it)
}

bias <- mean(run_many)-1/sqrt(1/2*pi)
eff <- mean((run_many-mean(run_many))^2)
mse <- mean((run_many-1/sqrt(1/2*pi))^2)
```
The random observation has bias `r round(bias,2)`, efficiency `r round(eff,2)` and mean square error `r round(mse,2)`.

# Run same with monte (part (i))
## Repetition 2: h=0.01
```{r}
set.seed(12345)
run_many <- c()
 for (x in 1:10000) {
  it <- monte(1000,h=0.01)
  run_many <- c(run_many,it)
}

bias <- mean(run_many)-1/sqrt(1/2*pi)
eff <- mean((run_many-mean(run_many))^2)
mse <- mean((run_many-1/sqrt(1/2*pi))^2)
```
The random observation has bias `r round(bias,2)`, efficiency `r round(eff,2)` and mean square error `r round(mse,2)`.

## Repetition 3: h=0.05
```{r}
set.seed(12345)
run_many <- c()
 for (x in 1:10000) {
  it <- monte(1000,h=0.05)
  run_many <- c(run_many,it)
}

bias <- mean(run_many)-1/sqrt(1/2*pi)
eff <- mean((run_many-mean(run_many))^2)
mse <- mean((run_many-1/sqrt(1/2*pi))^2)
```
The random observation has bias `r round(bias,2)`, efficiency `r round(eff,2)` and mean square error `r round(mse,2)`.

## Repetition 4: h=0.0001
```{r}
set.seed(12345)
run_many <- c()
 for (x in 1:10000) {
  it <- monte(1000,h=0.0001)
  run_many <- c(run_many,it)
}

bias <- mean(run_many)-1/sqrt(1/2*pi)
eff <- mean((run_many-mean(run_many))^2)
mse <- mean((run_many-1/sqrt(1/2*pi))^2)
```
The random observation has bias `r round(bias,2)`, efficiency `r round(eff,2)` and mean square error `r round(mse,2)`.      

